How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-06-15 Draft_June_2022/Full_draft_20220608.rmd
Added littels 2 x 2 table

                                      year), 1, 0))

@@

```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation", "Social Economic",
                                            "Sovereign Conservation", 
                                            "Economic Sovereignty", "Social Conservation", "Other")),
         con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0),
# model
model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_ei <- glm(EI_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_sd <- glm(SD_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_sov <- glm(sov_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
# # summary statistics, in appendix for now
# stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov,
#                      type = "text") # Negative for EI and SD
# # simple pooled OLS with time effects vs random effects
# ols <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
#                 data = ama_model, model = "pooling", index = c("year"))
# random <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
#                    data = ama_model, model = "random", index = c("year"))
# summary(ols)
# summary(random) # does not change when it comes independent variable
# # Colinearity test
# car::vif(model_logit_con) # All good!
# Plot model
ama_model$predicted_con = predict(model_logit_con, ama_model, type = "response")
# ama_model$predicted_ei = predict(model_logit_ei, ama_model, type = "response")
# ama_model$predicted_sd = predict(model_logit_sd, ama_model, type = "response")
# ama_model$predicted_sov = predict(model_logit_sov, ama_model, type = "response")
# Plot all regressions, just in case
# ama_model_all <- ama_model %>% 
#   pivot_longer(predicted_con:predicted_sov, names_to = "variable", values_to = "value")
# ggplot(ama_model_all, aes(x = km_to_manaus, y = value, color = variable)) +
#   geom_smooth(se = FALSE, size = .5)
ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) + 
  geom_jitter(alpha=.5)+
  geom_smooth(size = .5, color = "darkgreen") +
  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
  labs(x = "Distance from the Amazon (km)",
       y = "Share of environmental conservation",
       title = "Amazon constructions as an issue of environmental conservation\nin relation to distance from the Amazon",
       subtitle = "Distance as a straight line from state, or country, capital from the Amazon in kilometers",
       caption = "Curve in the plot is smoothed using loess method.") +
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))

>>>>

                                      year), 1, 0),
# # Table of Amazonian speeches internationally vs. in Brazil
# amazon_in_out <- pop %>% select(amazon_speech, location_cat)
# table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
# amazon_in_out <- mutate(amazon_in_out,
#                         location_cat = ifelse(grepl("International", location_cat), 0, 1))
# amazon_in_out <- table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
# rownames(amazon_in_out) <- c("Not Amazon Speech", "Amazon Speech")
# colnames(amazon_in_out) <- c("Outside of Brazil", "Within Brazil")
# amazon_in_out

@@

```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0))
# model
model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_ei <- glm(EI_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_sd <- glm(SD_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_sov <- glm(sov_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
# # summary statistics, in appendix for now
# stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov,
#                      type = "text") # Negative for EI and SD
# # simple pooled OLS with time effects vs random effects
# ols <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
#                 data = ama_model, model = "pooling", index = c("year"))
# random <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
#                    data = ama_model, model = "random", index = c("year"))
# summary(ols)
# summary(random) # does not change when it comes independent variable
# # Colinearity test
# car::vif(model_logit_con) # All good!
# Plot model
ama_model$predicted_con = predict(model_logit_con, ama_model, type = "response")
# ama_model$predicted_ei = predict(model_logit_ei, ama_model, type = "response")
# ama_model$predicted_sd = predict(model_logit_sd, ama_model, type = "response")
# ama_model$predicted_sov = predict(model_logit_sov, ama_model, type = "response")
# Plot all regressions, just in case
# ama_model_all <- ama_model %>% 
#   pivot_longer(predicted_con:predicted_sov, names_to = "variable", values_to = "value")
# ggplot(ama_model_all, aes(x = km_to_manaus, y = value, color = variable)) +
#   geom_smooth(se = FALSE, size = .5)
ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) + 
  geom_jitter(alpha=.5)+
  geom_smooth(size = .5, color = "darkgreen") +
  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
  labs(x = "Distance from the Amazon (km)",
       y = "The Amazon as an issue of environmental conservation",
       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance from Manaus",
       subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
       caption = "Curve in the plot is smoothed using loess method.") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
```
